On The Impact of Atoms of Confusion in JavaScript Code

### 2020-11-13 1_Introduction.tex
text improvements

\begin{figure*}
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\label{fig:lst01}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 in the left hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic
  as Control Flow} and \emph{Post-increment}. In the right hand side, we present the alternative code without atoms of confusion. We could simplify the code on the left even more, by replacing the \texttt{reduce} recursive pattern by a functional composition between the \texttt{filter} and
\texttt{length} patterns (e.g., \texttt{res = properties.filter(p => p).length}).}
\end{figure*}

>>>>

\begin{figure*}
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\label{fig:lst01}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 in the left hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic
  as Control Flow} and \emph{Post-increment}. In the right hand side, we present the alternative code without atoms of confusion. We could simplify the code on the left even more, by using \texttt{filter} and \texttt{length} instead of the \texttt{reduce} recursive pattern (e.g., \texttt{res = properties.filter(p => p).length}).}
\end{figure*}
